\documentclass[12pt, titlepage]{article}

\usepackage{fullpage}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{longtable}

\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}

\input{../../Comments}
\input{../../Common}

\newcounter{acnum}
\newcommand{\actheacnum}{AC\theacnum}
\newcommand{\acref}[1]{AC\ref{#1}}

\newcounter{ucnum}
\newcommand{\uctheucnum}{UC\theucnum}
\newcommand{\uref}[1]{UC\ref{#1}}

\newcounter{mnum}
\newcommand{\mthemnum}{M\themnum}
\newcommand{\mref}[1]{M\ref{#1}}

\begin{document}

\title{Module Guide for \progname{}} 
\author{\authname}
\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

\newpage

\section{Reference Material}

This section records information for easy reference.

\subsection{Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  AC & Anticipated Change\\
  DAG & Directed Acyclic Graph \\
  M & Module \\
  MG & Module Guide \\
  OS & Operating System \\
  R & Requirement\\
  SC & Scientific Computing \\
  SRS & Software Requirements Specification\\
  \progname & Explanation of program name\\
  UC & Unlikely Change \\
  \wss{etc.} & \wss{...}\\
  \bottomrule
\end{tabular}\\

\newpage

\tableofcontents

\listoftables

\listoffigures

\newpage

\pagenumbering{arabic}

\section{Introduction}

Decomposing a system into modules is a commonly accepted approach to developing
software.  A module is a work assignment for a programmer or programming
team~\citep{ParnasEtAl1984}.  We advocate a decomposition
based on the principle of information hiding~\citep{Parnas1972a}.  This
principle supports design for change, because the ``secrets'' that each module
hides represent likely future changes.  Design for change is valuable in SC,
where modifications are frequent, especially during initial development as the
solution space is explored.  

Our design follows the rules layed out by \citet{ParnasEtAl1984}, as follows:
\begin{itemize}
\item System details that are likely to change independently should be the
  secrets of separate modules.
\item Each data structure is implemented in only one module.
\item Any other program that requires information stored in a module's data
  structures must obtain it by calling access programs belonging to that module.
\end{itemize}

After completing the first stage of the design, the Software Requirements
Specification (SRS), the Module Guide (MG) is developed~\citep{ParnasEtAl1984}. The MG
specifies the modular structure of the system and is intended to allow both
designers and maintainers to easily identify the parts of the software.  The
potential readers of this document are as follows:

\begin{itemize}
\item New project members: This document can be a guide for a new project member
  to easily understand the overall structure and quickly find the
  relevant modules they are searching for.
\item Maintainers: The hierarchical structure of the module guide improves the
  maintainers' understanding when they need to make changes to the system. It is
  important for a maintainer to update the relevant sections of the document
  after changes have been made.
\item Designers: Once the module guide has been written, it can be used to
  check for consistency, feasibility, and flexibility. Designers can verify the
  system in various ways, such as consistency among modules, feasibility of the
  decomposition, and flexibility of the design.
\end{itemize}

The rest of the document is organized as follows. Section
\ref{SecChange} lists the anticipated and unlikely changes of the software
requirements. Section \ref{SecMH} summarizes the module decomposition that
was constructed according to the likely changes. Section \ref{SecConnection}
specifies the connections between the software requirements and the
modules. Section \ref{SecMD} gives a detailed description of the
modules. Section \ref{SecTM} includes two traceability matrices. One checks
the completeness of the design against the requirements provided in the SRS. The
other shows the relation between anticipated changes and the modules. Section
\ref{SecUse} describes the use relation between modules.

\section{Anticipated and Unlikely Changes} \label{SecChange}

This section lists possible changes to the system. According to the likeliness
of the change, the possible changes are classified into two
categories. Anticipated changes are listed in Section \ref{SecAchange}, and
unlikely changes are listed in Section \ref{SecUchange}.

\subsection{Anticipated Changes} \label{SecAchange}

Anticipated changes are the source of the information that is to be hidden
inside the modules. Ideally, changing one of the anticipated changes will only
require changing the one module that hides the associated decision. The approach
adapted here is called design for
change.

\begin{description}
\item[\refstepcounter{acnum} \actheacnum \label{acHardware}:] The specific
  hardware on which the software is running.
\item[\refstepcounter{acnum} \actheacnum \label{acInput}:] The format of the
  initial input data.
\item ...
\end{description}

\wss{Anticipated changes relate to changes that would be made in requirements,
design or implementation choices.  They are not related to changes that are made
at run-time, like the values of parameters.}

\subsection{Unlikely Changes} \label{SecUchange}

The module design should be as general as possible. However, a general system is
more complex. Sometimes this complexity is not necessary. Fixing some design
decisions at the system architecture stage can simplify the software design. If
these decision should later need to be changed, then many parts of the design
will potentially need to be modified. Hence, it is not intended that these
decisions will be changed.

\begin{description}
\item[\refstepcounter{ucnum} \uctheucnum \label{ucIO}:] Input/Output devices
  (Input: File and/or Keyboard, Output: File, Memory, and/or Screen).
\item ...
\end{description}

\section{Module Hierarchy} \label{SecMH}

This section provides an overview of the module design. Modules are summarized
in a hierarchy decomposed by secrets in Table \ref{TblMH}. The modules listed
below, which are leaves in the hierarchy tree, are the modules that will
actually be implemented.

\begin{description}
\item [\refstepcounter{mnum} \mthemnum \label{mHH}:] Hardware-Hiding Module
\item ...
\end{description}


\begin{table}[h!]
\centering
\begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Level 1} & \textbf{Level 2}\\
\midrule

{Hardware-Hiding Module} & ~ \\
\midrule

\multirow{7}{0.3\textwidth}{Behaviour-Hiding Module} & ?\\
& ?\\
& ?\\
& ?\\
& ?\\
& ?\\
& ?\\ 
& ?\\
\midrule

\multirow{3}{0.3\textwidth}{Software Decision Module} & {?}\\
& ?\\
& ?\\
\bottomrule

\end{tabular}
\caption{Module Hierarchy}
\label{TblMH}
\end{table}

\section{Connection Between Requirements and Design} \label{SecConnection}

The design of the system is intended to satisfy the requirements developed in
the SRS. In this stage, the system is decomposed into modules. The connection
between requirements and modules is listed in Table~\ref{TblRT}.

\wss{The intention of this section is to document decisions that are made
  ``between'' the requirements and the design.  To satisfy some requirements,
  design decisions need to be made.  Rather than make these decisions implicit,
  they are explicitly recorded here.  For instance, if a program has security
  requirements, a specific design decision may be made to satisfy those
  requirements with a password.}

\section{Module Decomposition} \label{SecMD}

Modules are decomposed according to the principle of ``information hiding''
proposed by \citet{ParnasEtAl1984}. The \emph{Secrets} field in a module
decomposition is a brief statement of the design decision hidden by the
module. The \emph{Services} field specifies \emph{what} the module will do
without documenting \emph{how} to do it. For each module, a suggestion for the
implementing software is given under the \emph{Implemented By} title. If the
entry is \emph{OS}, this means that the module is provided by the operating
system or by standard programming language libraries.  \emph{\progname{}} means the
module will be implemented by the \progname{} software.

Only the leaf modules in the hierarchy have to be implemented. If a dash
(\emph{--}) is shown, this means that the module is not a leaf and will not have
to be implemented.

\subsection{Hardware Hiding Modules (\mref{mHH})}

\begin{description}
\item[Secrets:]The data structure and algorithm used to implement the virtual
  hardware.
\item[Services:]Serves as a virtual hardware used by the rest of the
  system. This module provides the interface between the hardware and the
  software. So, the system can use it to display outputs or to accept inputs.
\item[Implemented By:] OS
\end{description}

\subsection{Behaviour-Hiding Module}

\begin{description}
\item[Secrets:]The contents of the required behaviours.
\item[Services:]Includes programs that provide externally visible behaviour of
  the system as specified in the software requirements specification (SRS)
  documents. This module serves as a communication layer between the
  hardware-hiding module and the software decision module. The programs in this
  module will need to change if there are changes in the SRS.
\item[Implemented By:] --
\end{description}

\subsubsection{Input Format Module (\mref{mInput})}

\begin{description}
\item[Secrets:]The format and structure of the input data.
\item[Services:]Converts the input data into the data structure used by the
  input parameters module.
\item[Implemented By:] [Your Program Name Here]
\item[Type of Module:] [Record, Library, Abstract Object, or Abstract Data Type]
  [Information to include for leaf modules in the decomposition by secrets tree.]
\end{description}

\subsubsection{Etc.}


\subsection{Software Decision Module}

\begin{description}
\item[Secrets:] The design decision based on mathematical theorems, physical
  facts, or programming considerations. The secrets of this module are
  \emph{not} described in the SRS.
\item[Services:] Includes data structure and algorithms used in the system that
  do not provide direct interaction with the user. 
  % Changes in these modules are more likely to be motivated by a desire to
  % improve performance than by externally imposed changes.
\item[Implemented By:] --
\end{description}

\subsubsection{Etc.}

\section{Traceability Matrix} \label{SecTM}

This section shows two traceability matrices: between the modules and the
requirements and between the modules and the anticipated changes.

% the table should use mref, the requirements should be named, use something
% like fref
\begin{table}[H]
\centering
\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Req.} & \textbf{Modules}\\
\midrule
R1 & \mref{mHH}, \mref{mInput}, \mref{mParams}, \mref{mControl}\\
R2 & \mref{mInput}, \mref{mParams}\\
R3 & \mref{mVerify}\\
R4 & \mref{mOutput}, \mref{mControl}\\
R5 & \mref{mOutput}, \mref{mODEs}, \mref{mControl}, \mref{mSeqDS}, \mref{mSolver}, \mref{mPlot}\\
R6 & \mref{mOutput}, \mref{mODEs}, \mref{mControl}, \mref{mSeqDS}, \mref{mSolver}, \mref{mPlot}\\
R7 & \mref{mOutput}, \mref{mEnergy}, \mref{mControl}, \mref{mSeqDS}, \mref{mPlot}\\
R8 & \mref{mOutput}, \mref{mEnergy}, \mref{mControl}, \mref{mSeqDS}, \mref{mPlot}\\
R9 & \mref{mVerifyOut}\\
R10 & \mref{mOutput}, \mref{mODEs}, \mref{mControl}\\
R11 & \mref{mOutput}, \mref{mODEs}, \mref{mEnergy}, \mref{mControl}\\
\bottomrule
\end{tabular}
\caption{Trace Between Requirements and Modules}
\label{TblRT}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{p{0.2\textwidth} p{0.6\textwidth}}
\toprule
\textbf{AC} & \textbf{Modules}\\
\midrule
\acref{acHardware} & \mref{mHH}\\
\acref{acInput} & \mref{mInput}\\
\acref{acParams} & \mref{mParams}\\
\acref{acVerify} & \mref{mVerify}\\
\acref{acOutput} & \mref{mOutput}\\
\acref{acVerifyOut} & \mref{mVerifyOut}\\
\acref{acODEs} & \mref{mODEs}\\
\acref{acEnergy} & \mref{mEnergy}\\
\acref{acControl} & \mref{mControl}\\
\acref{acSeqDS} & \mref{mSeqDS}\\
\acref{acSolver} & \mref{mSolver}\\
\acref{acPlot} & \mref{mPlot}\\
\bottomrule
\end{tabular}
\caption{Trace Between Anticipated Changes and Modules}
\label{TblACT}
\end{table}

\section{Use Hierarchy Between Modules} \label{SecUse}

In this section, the uses hierarchy between modules is
provided. \citet{Parnas1978} said of two programs A and B that A {\em uses} B if
correct execution of B may be necessary for A to complete the task described in
its specification. That is, A {\em uses} B if there exist situations in which
the correct functioning of A depends upon the availability of a correct
implementation of B.  Figure \ref{FigUH} illustrates the use relation between
the modules. It can be seen that the graph is a directed acyclic graph
(DAG). Each level of the hierarchy offers a testable and usable subset of the
system, and modules in the higher level of the hierarchy are essentially simpler
because they use modules from the lower levels.

\wss{The uses relation is not a data flow diagram.  In the code there will often
be an import statement in module A when it directly uses module B.  Module B
provides the services that module A needs.  The code for module A needs to be
able to see these services (hence the import statement).  Since the uses
relation is transitive, there is a use relation without an import, but the
arrows in the diagram typically correspond to the presence of import statement.}

\wss{If module A uses module B, the arrow is directed from A to B.}

\subsection*{Level 1: Foundational Modules}

\begin{itemize}
    \item \textbf{Label Database}
    \begin{itemize}
        \item \textbf{Secrets:} The storing and retrieving of data.
        \item \textbf{Services:} Allows connection by a database connector to facilitate the storage and retrieval of data.
    \end{itemize}
    \item \textbf{ImageObject Database}
    \begin{itemize}
        \item \textbf{Secrets:} The storing and retrieving of data.
        \item \textbf{Services:} Allows connection by a database connector to facilitate the storage and retrieval of data.
    \end{itemize}
    \item \textbf{Labeller Database}
    \begin{itemize}
        \item \textbf{Secrets:} The storing and retrieving of data.
        \item \textbf{Services:} Allows connection by a database connector to facilitate the storage and retrieval of data.
    \end{itemize}
\end{itemize}

\subsection*{Level 2: Database Connectors}

\begin{itemize}
    \item \textbf{Label Database Connector}
    \begin{itemize}
        \item \textbf{Uses:} Label Database
        \item \textbf{Secrets:} The steps to connect to and manipulate a database.
        \item \textbf{Services:} Connects to a database and executes pushing and fetching of data.
    \end{itemize}
    \item \textbf{ImageObject Database Connector}
    \begin{itemize}
        \item \textbf{Uses:} ImageObject Database
        \item \textbf{Secrets:} The steps to connect to and manipulate a database.
        \item \textbf{Services:} Connects to a database and executes pushing and fetching of data.
    \end{itemize}
    \item \textbf{Labeller Database Connector}
    \begin{itemize}
        \item \textbf{Uses:} Labeller Database
        \item \textbf{Secrets:} The steps to connect to and manipulate a database.
        \item \textbf{Services:} Connects to a database and executes pushing and fetching of data.
    \end{itemize}
\end{itemize}

\subsection*{Level 3: Core Services}

\begin{itemize}
    \item \textbf{Label Server}
    \begin{itemize}
        \item \textbf{Uses:} Label Database Connector
        \item \textbf{Secrets:} The steps to accept and store a label.
        \item \textbf{Services:} Converts a label JSON object and passes it to be stored in the database.
    \end{itemize}
    \item \textbf{Object Extraction Manager}
    \begin{itemize}
        \item \textbf{Uses:} Label Confidence Service, Object Extraction Service, Labeller Expertise Calculator
        \item \textbf{Secrets:} The algorithms used to aggregate labels into usable ImageObjects for model training.
        \item \textbf{Services:} Calls other modules to efficiently compute the most likely set of objects from a set of independent labels.
    \end{itemize}
    \item \textbf{Image Service Manager}
    \begin{itemize}
        \item \textbf{Uses:} Image Selection Service, Image Mask Service, Image Prior Analyzer
        \item \textbf{Secrets:} The algorithms used to select images to be served to a user.
        \item \textbf{Services:} Calls other modules to select the next images to be served to a user.
    \end{itemize}
\end{itemize}

\subsection*{Level 4: Specialized Services}

\begin{itemize}
    \item \textbf{Label Confidence Service}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to determine confidence in detected ImageObjects.
        \item \textbf{Services:} Calculates the confidence of a detected ImageObject.
    \end{itemize}
    \item \textbf{Object Extraction Service}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to extract ImageObjects.
        \item \textbf{Services:} Calculates the most likely ImageObjects from a set of labels and priors.
    \end{itemize}
    \item \textbf{Image Prior Analyzer}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to calculate ImagePriors.
        \item \textbf{Services:} Calculates the prior likelihood of a pixel being relevant.
    \end{itemize}
    \item \textbf{Labeller Expertise Calculator}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to calculate Labeller Expertise.
        \item \textbf{Services:} Calculates the expertise of a labeller in a given class using previous labels.
    \end{itemize}
    \item \textbf{Image Mask Service}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to modify a given image.
        \item \textbf{Services:} Modifies an image to improve labelling accuracy or efficiency.
    \end{itemize}
    \item \textbf{Image Selection Service}
    \begin{itemize}
        \item \textbf{Secrets:} The algorithms used to select the next image to show a user.
        \item \textbf{Services:} Selects an image to show to a given user.
    \end{itemize}
\end{itemize}

\subsection*{Directed Acyclic Graph (DAG)}

The following hierarchy is represented as a directed acyclic graph, with arrows showing the \textit{uses} relationship:

\begin{itemize}
    \item \textbf{Foundational Modules} (Label Database, ImageObject Database, Labeller Database)
    \begin{itemize}
        \item Used by their respective connectors.
    \end{itemize}
    \item \textbf{Database Connectors} (Label Database Connector, ImageObject Database Connector, Labeller Database Connector)
    \begin{itemize}
        \item Used by core services like Label Server, Object Extraction Manager, and Image Service Manager.
    \end{itemize}
    \item \textbf{Core Services} (Label Server, Object Extraction Manager, Image Service Manager)
    \begin{itemize}
        \item Use specialized services to provide advanced functionalities.
    \end{itemize}
    \item \textbf{Specialized Services} (Label Confidence Service, Object Extraction Service, Image Prior Analyzer, Labeller Expertise Calculator, Image Mask Service, Image Selection Service)
    \begin{itemize}
        \item Provide algorithms and computations needed by the core services.
    \end{itemize}
\end{itemize}

\begin{longtable}{|l|l|l|}
  \hline
  \textbf{Source Module} & \textbf{Target Module} & \textbf{Relationship} \\ \hline
  Label Database & Label Database Connector & Uses \\ \hline
  ImageObject Database & ImageObject Database Connector & Uses \\ \hline
  Labeller Database & Labeller Database Connector & Uses \\ \hline
  Label Database Connector & Label Server & Uses \\ \hline
  ImageObject Database Connector & Object Extraction Manager & Uses \\ \hline
  Labeller Database Connector & Object Extraction Manager & Uses \\ \hline
  Label Server & Label Database Connector & Uses \\ \hline
  Label Server & Label Confidence Service & Uses \\ \hline
  Object Extraction Manager & Label Confidence Service & Uses \\ \hline
  Object Extraction Manager & Object Extraction Service & Uses \\ \hline
  Object Extraction Manager & Labeller Expertise Calculator & Uses \\ \hline
  Image Service Manager & Image Selection Service & Uses \\ \hline
  Image Service Manager & Image Mask Service & Uses \\ \hline
  Image Service Manager & Image Prior Analyzer & Uses \\ \hline
  Label Confidence Service & N/A & Provides algorithms \\ \hline
  Object Extraction Service & N/A & Provides algorithms \\ \hline
  Image Prior Analyzer & N/A & Provides algorithms \\ \hline
  Labeller Expertise Calculator & N/A & Provides algorithms \\ \hline
  Image Mask Service & N/A & Provides algorithms \\ \hline
  Image Selection Service & N/A & Provides algorithms \\ \hline
  \end{longtable}

%\section*{References}

\section{User Interfaces}

\wss{Design of user interface for software and hardware.  Attach an appendix if
needed. Drawings, Sketches, Figma}

\section{Design of Communication Protocols}

\wss{If appropriate}

\section{Timeline}

\wss{Schedule of tasks and who is responsible}

\wss{You can point to GitHub if this information is included there}

\bibliographystyle {plainnat}
\bibliography{../../../refs/References}

\newpage{}

\end{document}